Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-24 article.tex
values for GENIE3

\begin{table}
\small
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline \hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\hline \hline
% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GENIE3 (depth = 1)     & 0.878 & & & & 0.184 & & & \\
GENIE3 (depth = 2)     & 0.889 & & & & 0.217 & & & \\
GENIE3 (depth = 3)     & & & & & & & & \\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\end{tabular}
\caption{TODO}
\label{tab:tab1}
\end{table}

>>>>

\begin{table}
\small
\centering
\begin{tabular}{@{}l *{8}{c}@{}}
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\hline \hline
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\hline \hline
% Directivity \textcolor{red}{appendix?} & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Pearson correlation    & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GENIE3 (depth = 1)     & 0.878 & 0.877 & 0.873 & 0.873 & 0.184 & 0.173 & 0.182& 0.172\\
GENIE3 (depth = 2)     & 0.889 & 0.888 & 0.883 & 0.884* & 0.217 & 0.210 & 0.220 & 0.199* \\
GENIE3 (depth = 3)     & 0.892 & 0.891* & 0.887 & 0.887 & 0.232 & 0.226* & 0.237 & 0.215\\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.930 &  0.927 &  0.926 &  0.923& 0.363  & 0.347 &  0.346 & 0.328 \\
Partial correlation (avg.) & 0.938 & 0.936 & 0.936 & 0.932& 0.391 & 0.389 & 0.385 & 0.374\\
% Our approach simple + dir & 0.939 & 0.936 & 0.937 & 0.933& 0.392 & 0.390 & 0.386 & 0.375\\
Partial correlation (opt.) & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach (opt. \& avg.)    & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
% Our approach + dir  \textcolor{red}{appendix?}   & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\end{tabular}
\caption{TODO (* means not 10000 trees but more than 9500, to be solved.) }
\label{tab:tab1}
\end{table}
